### 2022-01-26 src/text/2-package.tex
Adapt tex files
Add minted rule
Add more code examples

\subsection{Overview}
\begin{figure*}[t]
\centering
\includegraphics[width=1.\textwidth]{figures/data-flow-gammapy}
\caption{
Gammapy sub-package structure and data analysis workflow.
}
\label{fig:workflow}
\end{figure*}

@@

\begin{listing}
\begin{minted}{python}

from gammapy.data import DataStore

data_store = DataStore.from_dir("$GAMMAPY_DATA")
obs_ids = [1, 2, 3]
observations = data_store.get_observations(obs_ids)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

@@

\begin{listing}
\begin{minted}[numbers=right]{python}

from gammapy.makers import MapDatasetMaker

maker = MapDatasetMaker()
dataset = maker.run(dataset, observation)

\end{minted}
\caption{Using gammapy.data to access DL3 level data}
\label{codeexample:maker}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}

from astropy.coordinates import SkyCoord
from gammapy.maps import WcsGeom
from gammapy.datasets import MapDataset

skydir = SkyCoord("0d", "0d")
geom = WcsGeom.create(
	skydir=skydir, width="5 deg", binsz="0.2 deg"
)

dataset = MapDataset.create(
	geom=geom, name="my-dataset"
)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

@@

\begin{listing}
\begin{minted}[numbers=right]{python}

from gammapy.modeling.models import (
	SkyModel,
	PowerLawSpectralModel,
	PointSpatialModel
)

pwl = PowerLawSpectralModel()
point = PointSpatialModel()

model = SkyModel(
	spectral_model=pwl,
	spatial_model=point
	name="my-model"
)
\end{minted}
\caption{Using gammapy.data to access DL3 level data}
\label{codeexample:maker}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}

from gammapy.catalog import SOURCE_CATALOGS

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}

from gammapy.maps import Map
from astropy.coordinates import SkyCoord

skydir = SkyCoord("0d", "5d", frame="galactic")

# Create a WCS Map
m_wcs = Map.create(
	binsz=0.1, map_type='wcs', skydir=skydir, width=10.0
)

# Create a HPX Map
m_hpx = Map.create(
	binsz=0.1, map_type='hpx', skydir=skydir, width=10.0
)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

>>>>

\subsection{Overview}
\begin{figure*}[t]
\centering
\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
\caption{
Gammapy sub-package structure and data analysis workflow.
}
\label{fig:workflow}
\end{figure*}

@@

\begin{figure}

\import{code-examples/generated/}{gp_data}

\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{fig*:minted:gp_data}
\end{figure}

@@

\begin{figure}
\import{code-examples/generated/}{gp_makers}

\caption{Using gammapy.data to access DL3 level data}
\label{ig*:minted:gp_makers}
\end{figure}

@@

\begin{figure}

\import{code-examples/generated/}{gp_datasets}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{fig*:minted:gp_datasets}
\end{figure}

@@

\begin{figure}
\import{code-examples/generated/}{gp_models}
\caption{Using gammapy.modeling.models}
\label{fig*:minted:gp_models}
\end{figure}

@@

\begin{figure}
\import{code-examples/generated/}{gp_catalogs}
\caption{Using gammapy.catalogs}
\label{codeexample:data}
\end{figure}

@@

\begin{figure}

    \import{code-examples/generated/}{gp_maps}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{figure}
